Verification of the CVM algorithm with a Functional Probabilistic Invariant

### 2025-06-23 paper/sec/abstract.tex
make abstract slightly more grammatically correct?

Central to our formalization is a new proof technique based on \emph{functional probabilistic invariants}, which allows us to derive concentration bounds using the Cram\'{e}r--Chernoff method without relying on independence.
This simplifies the formal analysis considerably compared to the original proof by Chakraborty et al.
Moreover, our technique opens up the possible algorithm design space; we demonstrate this by introducing and verifying a new variant of the CVM algorithm that is total and unbiased---neither property is possessed by the original algorithm.
In this paper, we introduce the proof technique, describe its use in mechanizing both versions of the CVM algorithm in Isabelle/HOL, and present a supporting formalized library on negatively associated random variables used to verify the latter variant.
\end{abstract}

>>>>

Central to our formalization is a new proof technique based on functional probabilistic invariants, which allows us to derive concentration bounds using the Cram\'{e}r--Chernoff method without relying on independence.
This simplifies the formal analysis considerably compared to the original proof by Chakraborty et al.
Moreover, our technique opens up the possible algorithm design space; we demonstrate this by introducing and verifying a new variant of the CVM algorithm that is both total and unbiased---neither of which is a property of the original algorithm.
In this paper, we introduce the proof technique, describe its use in mechanizing both versions of the CVM algorithm in Isabelle/HOL, and present a supporting formalized library on negatively associated random variables used to verify the latter variant.
\end{abstract}
